Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-06 ms.tex
fixing up explanation of units

This equation is quite similar to Equation \ref{equ:broadband}, but with two 
important differences. The first is that the normalization of 
$\tilde{I}_{\nu_i}$ is now specified by $\tilde{I}_{545}$, which represents the
 broadband intensity measured in \PLANCK~545 GHz. Also, each term in the 
numerator is multiplied by a conversion factor $u_{\nu_i}^{-1}(T_k, \beta_k)$. 
This factor is necessary because some of the \PLANCK~maps of interest have 
units of $K_{CMB}$ (100-353 GHz), while others (545-3000 GHz) have units of 
MJy/sr. Therefore, we wish to predict the low frequency bands in $K_{CMB}$, and
the high frequency bands in MJy/sr. For this reason, we evaluate $B_{\nu_i}$ in
Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for all 
$\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the conversion factor from $K_{CMB}$ to MJy/sr

@@

The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent.

@@

The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
\verb|i100| and the higher frequency HFI maps are provided in units of 
MJy/sr. We will treat the SED normalization $\tilde{I}_{545}$ as a free 
parameter in our fitting procedure. In our baseline fits, second free parameter
 is $T_2$, which determines the shape of the SED through $M_{\nu}$ as well as 
$b_{\nu_i}(T_2)$.

>>>>

This equation is quite similar to Equation \ref{equ:broadband}, but with two 
important differences. First, the normalization of $\tilde{I}_{\nu_i}$ is now 
specified by $\tilde{I}_{545}$, which represents the broadband intensity 
measured in the \PLANCK~545 GHz band. The denominator serves to ensure that,
for the case of $\nu_i$=545 GHz, $\tilde{I}_{545}$ is self-consistent. Second, 
each term in the numerator is multiplied by a conversion factor 
$u_{\nu_i}^{-1}(T_k, \beta_k)$. This factor is necessary because some of the 
\PLANCK~maps of interest have units of $K_{CMB}$ (100-353 GHz), while the
remaining maps (545-3000 GHz) have units of MJy/sr. Complicating matters, the 
conversion from $K_{CMB}$ to MJy/sr depends on the spectrum under 
consideration; attempting to apply conversion factors to put all of the 
observed maps themselves into common units is not a particularly attractive 
option. Therefore, we adopt the strategy of predicting each band in its native 
units, whether MJy/sr or $K_{CMB}$. For this reason, we always evaluate 
$B_{\nu_{i,c}}$ in Equation \ref{eqn:inten} in MJy/sr and let $u_{\nu_i}$=1 for
all $\nu_i$$\ge$545 GHz. For $\nu_i$$\le$353 GHz, $u_{\nu_i}(T_k, \beta_k)$ 
represents the appropriate conversion factor from $K_{CMB}$ to MJy/sr.

@@

@@

%The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
%\verb|i100| and the higher frequency HFI maps are provided in units of 
%MJy/sr.

We will treat the SED normalization $\tilde{I}_{545}$ as a free 
parameter in our fitting procedure. In our baseline fits, second free parameter
 is $T_2$, which determines the shape of the SED through $M_{\nu}$ as well as 
$b_{\nu_i}(T_2)$.
